---
title: "BIS data dashboard"
output: 
  flexdashboard::flex_dashboard:
    theme: bootstrap
    orientation: columns
    vertical_layout: scroll
    source_code: embed
    navbar:
      - { title: "BIS Statistics", href: "https://www.bis.org/statistics/", align: right }
      - { title: "BIS Statistics Explorer", href: "https://stats.bis.org/statx/", align: right }
      - { title: "BIS Statistics Warehouse", href: "http://stats.bis.org/bis-stats-tool/", align: right }
      - { title: "Raw data", href: "https://www.bis.org/statistics/full_data_sets.htm", align: right }
params:
  ctr: "JP"
---

```{css, echo = FALSE}
p.caption {
  font-size: 0.8em;
  font-style: italic;
  color: grey;
  margin-right: 10%;
  margin-left: 10%;  
  text-align: justify;
}

.js-plotly-plot,
.plot-container {
  height: 32vh;
  width: 24vw;
}
```

```{r include = FALSE}
# Uncomment this to refresh data
#source("refresh_bis_data.R")

source("bis_helper_functions.R")
load("bis_stats.RData")

#ctr       <- "JP"
ctr       <- params$ctr
refctr    <- sort(c("US", "XM", "DE", "JP", "GB", "CH", "CA"))
startdate <- as.Date("2000-01-01")

ctrn      <- countrycode(ctr, "iso2c", "country.name",
                         custom_match = c("XM" = "Euro Area"))
ctrs      <- paste(paste(ctrn, paste0("(", ctr, ")")), collapse = ", ")
refctrn   <- countrycode(refctr, "iso2c", "country.name",
                         custom_match = c("XM" = "Euro Area"))
refctrs   <- paste(paste(refctrn, paste0("(", refctr, ")")), collapse = ", ")
```

# Information {.sidebar}

**Economy:** `r ctrs`

**Reference economies:** `r refctrs`

**Plots start:** `r startdate`

**Last data update:** `r lastrefresh`

This dashboard is not officially related to, or endorsed by, the BIS.

[Source on GitHub](https://github.com/stefanangrick/)

# `r ctrn`

## Column 1

### Credit to the private nonfinancial sector

```{r echo = FALSE, fig.cap = "Source: [Bank for International Settlements](stats.bis.org/statx/toc/CRE.html)"}
creData <- GetCreData(cre, ctr, refctr)
if (!is.null(creData)) {
  PlotlyLine(creData, hghlght = ctr, ylab = "% of GDP", startdate = startdate)  
}
```

`r if(is.null(creData)){"No data available"}`

### Credit to the private nonfinancial sector: Households and Nonfinancial corporations

```{r echo = FALSE, fig.cap = "Note: H = households, N = nonfinancial corporations; Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/CRE.html)"}
creDataSect <- GetCreDataSect(cre, ctr, NULL)
if (!is.null(creDataSect)) {
  PlotlyBar(creDataSect, ylab = "% of GDP", bmode = "relative",
            startdate = startdate)
}
```

`r if(is.null(creDataSect)){"No data available"}`

### Bank share of total credit to private nonfinancial sector

```{r echo = FALSE, fig.cap = "Source: [Bank for International Settlements](stats.bis.org/statx/toc/CRE.html)"}
creDataBankshare <- GetCreDataBankshare(cre, ctr, refctr)
if (!is.null(creDataBankshare)) {
  PlotlyLine(creDataBankshare, hghlght = ctr, ylab = "% of total credit",
             startdate = startdate)  
}
```

`r if(is.null(creDataBankshare)){"No data available"}`

### Credit-to-GDP gap (actual-trend)

```{r echo = FALSE, fig.cap = "Source: [Bank for International Settlements](stats.bis.org/statx/toc/CTG.html)"}
ctgData <- GetCtgData(ctg, ctr, refctr)
if (!is.null(ctgData)) {
  PlotlyLine(ctgData, hghlght = ctr, ylab = "% of GDP", startdate = startdate)
}
```

`r if(is.null(ctgData)){"No data available"}`

### Credit-to-GDP: Ratio (actual data) & trend (HP filter)

```{r echo = FALSE, fig.cap = "Note: A = actual data, B = trend (HP filter with lambda = 400,000); Source: [Bank for International Settlements](stats.bis.org/statx/toc/CTG.html)"}
ctgDataActualtrend <- GetCtgDataActualtrend(ctg, ctr)
if (!is.null(ctgDataActualtrend)) {
  PlotlyLine(ctgDataActualtrend, ylab = "% of GDP", startdate = startdate)
}
```

`r if(is.null(ctgDataActualtrend)){"No data available"}`

### Debt service ratio: Private nonfinancial sector

```{r echo = FALSE, fig.cap = "Note: Interest payments and amortisation to income; Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/DSR.html)"}
dsrData <- GetDsrData(dsr, ctr, refctr)
if (!is.null(dsrData)) {
  PlotlyLine(dsrData, hghlght = ctr, ylab = "Debt service / Income (%)",
             startdate = startdate)
}
```

`r if(is.null(dsrData)){"No data available"}`

### Debt service ratio: Households and Nonfinancial corporations

```{r echo = FALSE, fig.cap = "Note: Interest payments and amortisation to income; H = households, N = nonfinancial corporations; Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/DSR.html)"}
dsrDataSect <- GetDsrDataSect(dsr, ctr, NULL)
if (!is.null(dsrDataSect)) {
  PlotlyBar(dsrDataSect, ylab = "Debt service / Income (%)", bmode = "group",
            startdate = startdate)
}
```

`r if(is.null(dsrDataSect)){"No data available"}`

### US dollar exchange rates

```{r echo = FALSE, fig.cap = "Note: LCU/USD (in hundreds of JPY for Japan); monthly average; Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/XR.html)"}
xruData <- GetXruData(xru, ctr, refctr)
if (!is.null(xruData)) {
  PlotlyLine(xruData, hghlght = ctr, ylab = "LCU/USD", startdate = startdate)  
}
```

`r if(is.null(xruData)){"No data available"}`

### Nominal effective exchange rate (narrow)

```{r echo = FALSE, fig.cap = "Note: Increase = appreciation; monthly average; Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/XR.html)"}
eerData <- GetEerData(eer, ctr, refctr)
if (!is.null(eerData)) {
  PlotlyLine(eerData, hghlght = ctr, ylab = "Index, 2010 = 100",
             startdate = startdate)
}
```

`r if(is.null(eerData)){"No data available"}`

### Central bank policy rates

```{r echo = FALSE, fig.cap = "Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/CBP.html)"}
cbpData <- GetCbpData(cbp, ctr, refctr)
if (!is.null(cbpData)) {
  PlotlyLine(cbpData, hghlght = ctr, ylab = "%", startdate = startdate)
}
```

`r if(is.null(cbpData)){"No data available"}`

### Consumer prices

```{r echo = FALSE, fig.cap = "Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/CPI.html)"}
cpiData <- GetCpiData(cpi, ctr, refctr)
if (!is.null(cpiData)) {
  PlotlyLine(cpiData, hghlght = ctr,
             ylab = "% year-on-year", startdate = startdate)
}
```

`r if(is.null(cpiData)){"No data available"}`

### Property prices

```{r echo = FALSE, fig.cap = "Note: Interest payments and amortisation to income; long series and selected series combined; Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/SPP.html)"}
sppData <- GetSppData(spp, lpp, ctr, refctr)
if (!is.null(sppData)) {
  PlotlyLine(sppData, hghlght = ctr, 
             ylab = "Index, 2010 = 100", startdate = startdate)
}
```

`r if(is.null(sppData)){"No data available"}`

## Column 2

### Claims on `r ctrn`, by currency

```{r echo = FALSE, fig.cap = "Note: UN9 = unallocated; based on LBS (used to judge currency composition of banks' balance sheets, not exposures); Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/LBS.html)"}
lbsDataCurr <- GetLbsDataCurr(lbs, ctr, lpos = "C")
if (!is.null(lbsDataCurr)) {
  PlotlyBar(lbsDataCurr, ylab = "USD", startdate = startdate)
}
```

`r if(is.null(lbsDataCurr)){"No data available"}`

### Liabilities to `r ctrn`, by currency

```{r echo = FALSE, fig.cap = "Note: UN9 = unallocated; based on LBS (used to judge currency composition of banks' balance sheets, not exposures); Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/LBS.html)"}
lbsDataCurr <- GetLbsDataCurr(lbs, ctr, lpos = "L")
if (!is.null(lbsDataCurr)) {
  PlotlyBar(lbsDataCurr, ylab = "USD", startdate = startdate)
}
```

`r if(is.null(lbsDataCurr)){"No data available"}`

### Claims on `r ctrn`, by instrument

```{r echo = FALSE, fig.cap = "Note: A = all, D = debt securities, G = loans and deposits, I = other, U = unallocated; based on LBS (used to judge currency composition of banks' balance sheets, not exposures); Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/LBS.html)"}
lbsDataInstrC <- GetLbsDataInstr(lbs, ctr, lpos = "C")
if (!is.null(lbsDataInstrC)) {
  PlotlyBar(lbsDataInstrC, ylab = "USD", startdate = startdate)
}
```

`r if(is.null(lbsDataInstrC)){"No data available"}`

### Liabilities to `r ctrn`, by instrument

```{r echo = FALSE, fig.cap = "Note: A = all, D = debt securities, G = loans and deposits, I = other, U = unallocated; based on LBS (used to judge currency composition of banks' balance sheets, not exposures); Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/LBS.html)"}
lbsDataInstrL <- GetLbsDataInstr(lbs, ctr, lpos = "L")
if (!is.null(lbsDataInstrL)) {
  PlotlyBar(lbsDataInstrL, ylab = "USD", startdate = startdate)
}
```

`r if(is.null(lbsDataInstrL)){"No data available"}`

### Claims on `r ctrn`, by country

```{r echo = FALSE, fig.cap = "Note: Based on LBS (used to judge currency composition of banks' balance sheets, not exposures); Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/LBS.html)"}
lbsDataCtrC <- GetLbsDataCtr(lbs, ctr, lpos = "C")
if (!is.null(lbsDataCtrC)) {
  PlotlyBar(lbsDataCtrC, ylab = "USD", startdate = startdate)
}
```

`r if(is.null(lbsDataCtrC)){"No data available"}`

### Liabilities to `r ctrn`, by country

```{r echo = FALSE, fig.cap = "Note: Based on LBS (used to judge currency composition of banks' balance sheets, not exposures); Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/LBS.html)"}
lbsDataCtrL <- GetLbsDataCtr(lbs, ctr, lpos = "L")
if (!is.null(lbsDataCtrL)) {
  PlotlyBar(lbsDataCtrL, ylab = "USD", startdate = startdate)
}
```

`r if(is.null(lbsDataCtrL)){"No data available"}`

### Claims on `r ctrn`, consolidated, immediate counterparty, by country

```{r echo = FALSE, fig.cap = "Note: Based on CBS, immediate counterparty basis (used to judge country risk exposure); Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/CBS.html)"}
cbsDataIcCtr <- GetCbsDataIcCtr(cbs, ctr)
if (!is.null(cbsDataIcCtr)) {
  PlotlyBar(cbsDataIcCtr, ylab = "USD", startdate = startdate)
}
```

`r if(is.null(cbsDataIcCtr)){"No data available"}`

### Market share of foreign banks' subsidiaries

```{r echo = FALSE, fig.cap = "Note: Based on CBS, immediate counterparty basis (used to judge country risk exposure); Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/CBS.html)"}
cbsDataIcCtrForeignbankshare <-
  GetCbsDataIcCtrForeignbankshare(cbs, ctr, refctr)
if (!is.null(cbsDataIcCtrForeignbankshare)) {
  PlotlyLine(cbsDataIcCtrForeignbankshare, hghlght = ctr,
             ylab = "% of total claims, immediate counterparty",
             startdate = startdate)  
}
```

`r if(is.null(cbsDataIcCtrForeignbankshare)){"No data available"}`

### Claims on `r ctrn`, consolidated, ultimate risk basis, by country

```{r echo = FALSE, fig.cap = paste0("Note: Based on CBS, ultimate risk basis (includes lending to affiliates of ", ctrn, " outside of ", ctrn, " that might be guaranteed by parent within ", ctrn, ", i.e. net of risk transfers; used to judge country risk exposure); Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/CBS.html)")}
cbsDataUrCtr<- GetCbsDataUrCtr(cbs, ctr)
if (!is.null(cbsDataUrCtr)) {
  PlotlyBar(cbsDataUrCtr, ylab = "USD", startdate = as.Date("2005-01-01"))
}
```

`r if(is.null(cbsDataUrCtr)){"No data available"}`

### Claims on `r ctrn`, consolidated, ultimate risk basis, by sector + other potential exposures

```{r echo = FALSE, fig.cap = "Note: B = banks, O = official, R = non-bank private sector; V = derivatives, W = guarantees extended, X = credit commitments; based on CBS, ultimate risk basis + other potential exposures (used to judge country risk exposure); Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/CBS.html)"}
cbsDataUrSect <- GetCbsDataUrSect(cbs, ctr)
if (!is.null(cbsDataUrSect)) {
  PlotlyBar(cbsDataUrSect, ylab = "USD", startdate = as.Date("2005-01-01"))
}
```

`r if(is.null(cbsDataUrSect)){"No data available"}`

### Domestic and international debt securities, resident issuers

```{r echo = FALSE, fig.cap = "DDS = domestic debt securities (difference between total and international debt securities), IDS = international debt securities (D = domestic currency, USD = USD, EU1 = EUR, F = other foreign currency); Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/SEC.html)"}
secDataRes <- GetSecDataRes(sec, ctr)
if (!is.null(secDataRes)) {
  PlotlyBar(secDataRes, ylab = "USD", startdate = startdate)
}
```

`r if(is.null(secDataRes)){"No data available"}`

### International debt securities, national issuers

```{r echo = FALSE, fig.cap = "OTH = other currencies; Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/SEC.html)"}
secDataNatl <- GetSecDataNatl(sec, ctr)
if (!is.null(secDataNatl)) {
  PlotlyBar(secDataNatl, ylab = "USD", startdate = startdate)
}
```

`r if(is.null(secDataNatl)){"No data available"}`

# Global

## Column 1

### International debt securities by currency of denomination

```{r echo = FALSE, fig.cap = "OTH = other currencies; national and resident concepts are equivalent at world level; Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/SEC.html)"}
PlotlyBar(GetSecDataCurr(sec), ylab = "USD", startdate = startdate)
```

### Global liquidity: Total credit to non-bank borrowers, USD

```{r echo = FALSE, fig.cap = "Based on global liquidity indicators (highly correlated with booms/busts in financial conditions); Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/GLI.html)"}
PlotlyLine(GetGliData(gli, "USD"), ylab = "USD", startdate = startdate)
```

### Global liquidity: Total credit to non-bank borrowers, EUR

```{r echo = FALSE, fig.cap = "Based on global liquidity indicators (highly correlated with booms/busts in financial conditions); Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/GLI.html)"}
PlotlyLine(GetGliData(gli, "EUR"), ylab = "EUR", startdate = startdate)
```

### Global liquidity: Total credit to non-bank borrowers, JPY

```{r echo = FALSE, fig.cap = "Based on global liquidity indicators (highly correlated with booms/busts in financial conditions); Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/GLI.html)"}
PlotlyLine(GetGliData(gli, "JPY"), ylab = "JPY", startdate = startdate)
```

### FX turnover by currency, triennial survey

```{r echo = FALSE, fig.cap = "OTH = other currencies; Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/DER.html)"}
PlotlyBar(GetDerData(der), ylab = "USD", startdate = startdate)
```

## Column 2

### Notional amounts OTC derivatives outstanding, by risk category

```{r echo = FALSE, fig.cap = "U = other derivatives, D = interest rate, E = equity, T = credit derivatives, J = commodities, B = foreign exchange; notional amounts outstanding; Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/DER.html)"}
PlotlyBar(GetOtcDataRisk(otc), ylab = "USD", startdate = startdate)
```

### Gross market value of OTC interest rate derivatives, by currency

```{r echo = FALSE, fig.cap = "Note: Notional amounts outstanding; Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/DER.html)"}
PlotlyBar(GetOtcDataCurr(otc), ylab = "USD", startdate = startdate)
```

### Outstanding notional amount of CDS, by sector of counterparty

```{r echo = FALSE, fig.cap = "A = Total (all counterparties), B = reporting dealers, K = central counterparties; Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/DER.html)"}
PlotlyLine(GetOtcDataCDSSect(otc), ylab = "USD",
           startdate = as.Date("2005-01-01"))
```

### Exchange-traded interest rate derivatives, turnover by currency

```{r echo = FALSE, fig.cap = "Average daily turnover, notional amounts, 3-month moving averages; Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/DER.html)"}
PlotlyBar(GetXtdData(xtd, riskcat = "C", mak = 3), ylab = "USD",
          startdate = startdate)
```

### Exchange-traded foreign exchange derivatives, turnover by currency

```{r echo = FALSE, fig.cap = "Average daily turnover, notional amounts, 3-month moving averages; Source: [Bank for International Settlements](https://stats.bis.org/statx/toc/DER.html)"}
PlotlyBar(GetXtdData(xtd, riskcat = "B", mak = 3), ylab = "USD",
          startdate = startdate)
```

